\documentclass[10pt]{cls/LaTeX-Class-File-for-Research-Report-Formats-of-Mahidol-University}
\usepackage[utf8]{inputenc}
\graphicspath{ {images/} }
\begin{document}
\typeOfReport{thematic} %thesis %thematic
\title{an implementation of latex class file for research report formats of mahidol university}
\titleThai{\begin{thai} การพัฒนาคลาสของ Latex เพื่อใช้ในการจัดรูปแบบรูปเล่ม วิทยานิพนธ์ หรือ สารนิพนธ์ ของมหาวิทยาลัยมหิดล  \end{thai}}
\author{Test Name-Lastname}
\authorThai{\begin{thai} ทดสอบ ชื่อ-นามสกุล \end{thai}}
\degreefaculty{M.Sc. (Information Technology Management)}
\degreefacultyThai{\begin{thai} วท.ม. (การจัดการเทคโนโลยีสารสนเทศ) \end{thai}}
\ProgramTitle{a thematic paper submitted in partial fulfillment of the requirements for the degree of master of science (information technology management) faculty of graduate study mahidol university 2017}
\DegreeTitle{Thematic Paper}
\SubmittedFor{Master of Science (Information Technology Management)}
\SubmittedDate{January 1, 2017}
\Advisor{Lect. Somchai Saijai, Ph.D. (Electrical Engineering)}
\CoAdvisor{Asst. Prof. Sakarin Daoray, Ph.D. (Electrical and Computer Engineering)}
\Committee{Asst. Prof. Sakarin Daoray, Ph.D. (Electrical and Computer Engineering)}
\CommitteePosition{Program Director Master of Science Program in Information Technology Management Faculty of Engineering Mahidol University}
\dean{Prof. Precha Prache, M.D.,Ph.D. (Biochemistry)}
\deanPo{Faculty of Graduate Studies, Mahidol University}
\deanAct{Asst. Prof. Warakorn Charoensuk, Ph.D. (Electical Engineering)}
\deanActPo{Faculty of Graduate Studies, Mahidol University}
\memberOne{Lect. Somboon Boonnad Ph.D. (Information Technology)}
\memberTwo{Asst. Prof. Kaijoh Brother, Ph.D. (Electrial and Computer Engineering)}
\memberThree{Asst. Prof. Sakarin Daoray, Ph.D. (Electrical and Computer Engineering)}

\referencesOrBibliography{References} %change name of title References Or Bibliography

\maketitle

\input{abstract}
\input{acknowledgement}

%%%%% please use it for header numbering mahidol style %%%%%
\maketitle
\tableofcontents
\listoftables
\listoffigures
\pagestyle{mahidol-fancy-style}

\input{chapter1}
\input{chapter2}
\input{chapter3}
%\input{chapter4}
%\input{chapter5}
\input{references}
\input{appendices}
\input{biography}

\end{document} %%%%%%%%%%  do not put anything after this
